---
title: "R Notebook"
output: html_notebook
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
library(tidyverse)
library(TTR)
library(quantmod)
library(PerformanceAnalytics)
library(RColorBrewer)
library(tseries)
library(lubridate)
library(Quandl)
Quandl.api_key("zrcB2Ejv9UmvhPCUsy2_")
options("getSymbols.yahoo.warning"=FALSE)

```

#Introduction:  We will load the libraries and capture some data for a stock and do a quick line graph

```{r}
MSFT <- getSymbols("MSFT", auto.assign = FALSE)
head(MSFT)
dim(MSFT)
```

# Our first task will be to download daily returns for a new Stock.  We can start with Amazon.
```{r}

```

# Let's look at the Head and Tail of the Df
```{r}
head(MSFT)
tail(MSFT)
dim(MSFT)
str(MSFT)
class(MSFT)
```

# In this task we're going to learn subsetting fundementals. We can do it by row/column reference or by row/column name

```{r}
df <- as.data.frame(MSFT)
class(df)
head(df)
dim(df)
str(df)

df <- as.xts(df)
class(df)

write.csv(df,"newdataMSFT.csv")
```

#In this task I am going to show you how to rename the columns or easier subsetting.  I am also going to show you how to save data into .csv file for import into excel.  

```{r}

```



# In this task we will learn about xts. zoo objects and how to convert back and forth between xts and data frames.

```{r}

```


# In this task we will create a Daily Return and then Chart the data for one stock.

```{r}
tsla <- getSymbols("TSLA",auto.assign = FALSE)
head(tsla)


head(dailyReturn(tsla$TSLA.Adjusted))

plot(dailyReturn(tsla$TSLA.Adjusted,type="l"))
```

#Next Project will consist of more data analytics and comparing multiple stocks against each other.
```{r}
msft <- getSymbols("MSFT" , auto.assign = FALSE)

msft_Ad <- Ad(msft)
head(msft_Ad)

msft_daily <- dailyReturn(msft_Ad)
head(msft_daily)

new_msft <- dailyReturn(getSymbols("MSFT",auto.assign = F))
head(new_msft)
```

```{r}
meta <- getSymbols("META",auto.assign = F)
head(meta)

meta_Ad <- meta$META.Adjusted
head(meta_Ad)

meta_daily <- dailyReturn(meta_Ad)
dim(meta_daily)

new_meta <- dailyReturn(Ad(getSymbols("META",auto.assign = F)))
```

```{r}
comb <- merge(new_msft,new_meta)
head(comb)

comb_traded <- merge(new_msft,new_meta,all = F)
head(comb_traded)
dim(comb_traded)
```
```{r}
charts.PerformanceSummary(comb_traded, main = "META vs MSFT")
```


```{r}
table.AnnualizedReturns(comb_traded,
                        scale =252, 
                        Rf =0.004/252)
```

